---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}
library(leaflet)
m = leaflet() %>% setView(lng=121.5, lat=25.05, zoom=13) 
m = m |> addTiles()
m = m |> leaflet::addCircleMarkers(lng=121.5, lat=25.05)
m
```

```{r, eval=FALSE, include=F}
m$x$calls
# leaflet object widget 
m |> econIDV::LeafletTools() -> lf

lf$calls[[1]]() |> clipr::write_clip()
lf$calls[[2]]()
# translate all m$x$calls element to js
# clipr::write_clip() puts all character vector in your clipboard
lf$allCalls() |> clipr::write_clip()
```


Column {data-width=650}
-----------------------------------------------------------------------

### Chart B

```{r}
htmltools::div(
  id="map", style="height:100%;"
)
```

```{js}
// initiate map
m = L.map("map").setView([25.05,121.5],13)

// addTiles
t = L.tileLayer(...["https://{s}.tile.openstreetmap.org/{z}/{x}/{y}.png",{"minZoom":0,"maxZoom":18,"tileSize":256,"subdomains":"abc","errorTileUrl":"","tms":false,"noWrap":false,"zoomOffset":0,"zoomReverse":false,"opacity":1,"zIndex":1,"detectRetina":false,"attribution":"&copy; <a href=\"https://openstreetmap.org\">OpenStreetMap<\/a> contributors, <a href=\"https://creativecommons.org/licenses/by-sa/2.0/\">CC-BY-SA<\/a>"}])
t.addTo(m)
// addCircleMarkers
args={"lat":25.05,"lng":121.5,"radius":10,"markerOptions":{"radius":10,"interactive":true,"className":"","stroke":true,"color":"#03F","weight":5,"opacity":0.5,"fill":true,"fillColor":"#03F","fillOpacity":0.2},"popupContent":{},"popupOptions":{"interactive":false,"permanent":false,"direction":"auto","opacity":1,"offset":[0,0],"textsize":"10px","textOnly":false,"className":"","sticky":true}}
latLng = L.latLng(args.lat,args.lng)
mk = L.circleMarker(latLng, args.markerOptions)

mk.addTo(m)
