---
title: "week8"
output: html_document
date: "2023-04-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)
```

# Path

-   absolute path: `C:\...`

-   relative path: relative to project folder

    -   "./": project root

    -   "../": one level of parent folder up relative to the current file that uses the specification.

        -   week8.R in week8/. Its one level of parent folder up is `111-2-interactive-data-visualization`

# econIDV

```{r}
plot_ly() |>
    do_add_trace(traces[[1]]) |>
    do_add_trace(traces[[2]]) |>
    do_add_trace(traces[[4]]) 
```

-   Select `traces[[1]]` and copy (to your clipboard)

-   Addins \> econIDV: get name=value pairs from a list

    ```{r}
    plot_ly() |>
      add_trace(
        # paste
        x = traces[[1]]$x,
        y = traces[[1]]$y,
        text = traces[[1]]$text,
        type = traces[[1]]$type,
        mode = traces[[1]]$mode,
        marker = traces[[1]]$marker,
        hoveron = traces[[1]]$hoveron,
        name = traces[[1]]$name,
        legendgroup = traces[[1]]$legendgroup,
        showlegend = traces[[1]]$showlegend,
        xaxis = traces[[1]]$xaxis,
        yaxis = traces[[1]]$yaxis,
        hoverinfo = traces[[1]]$hoverinfo,
        frame = traces[[1]]$frame
      ) |>
      add_trace(
        # paste
        x = traces[[2]]$x,
        y = traces[[2]]$y,
        text = traces[[2]]$text,
        type = traces[[2]]$type,
        mode = traces[[2]]$mode,
        marker = traces[[2]]$marker,
        hoveron = traces[[2]]$hoveron,
        name = traces[[2]]$name,
        legendgroup = traces[[2]]$legendgroup,
        showlegend = traces[[2]]$showlegend,
        xaxis = traces[[2]]$xaxis,
        yaxis = traces[[2]]$yaxis,
        hoverinfo = traces[[2]]$hoverinfo,
        frame = traces[[2]]$frame
      ) |>
      add_trace(
        x = traces[[4]]$x,
        y = traces[[4]]$y,
        text = traces[[4]]$text,
        type = traces[[4]]$type,
        mode = traces[[4]]$mode,
        line = traces[[4]]$line,
        hoveron = traces[[4]]$hoveron,
        showlegend = traces[[4]]$showlegend,
        xaxis = traces[[4]]$xaxis,
        yaxis = traces[[4]]$yaxis,
        hoverinfo = traces[[4]]$hoverinfo,
        frame = traces[[4]]$frame
      )
    ```

# Filter

Compared to **highlight** which dim non-selected traces and highlighted the selected trace, **filter** clears the graph and shows only the filtered data.

Filter and highlight are actually provided by **crosstalk** package which **plotly** take advantage of its **filter and selection** functions.

-   [using crosstalk](https://rstudio.github.io/crosstalk/using.html)

## Selectize.js

`crosstalk::filter_xxx` uses **selectize.js** which can be accessed through the DOM's selectize interface.

```{js}
/* choose all DOM with select tag */
selectDOM = document.querySelector("#country select")

control = selectDOM.selectize

control.setValue(["Argentina"])
```
